|

### 2022-03-11 Memo/Memo_Template.Rmd
update AJPS revision

---
We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript. We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result. Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews. We adopt the following conventions:

\begin{itemize}
\item Suggestions identified in reviewers' reports are in \textit{italicized text}. We provide direct quotation of their reviewers' reports, which have been lightly edited for clarifications or to conserve space.
\item Our responses to the reviewers' suggestions are in standard text.
\item The specific locations in the manuscript and online appendix where incorporated
revisions can be found are shown in \textbf{bold text}.
\end{itemize}

@@

\vspace{.2cm}
We thank the reviewer 1 for these two relevant additions. We cite \citet{GilliganMatsusaka2001} article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p. 85]{gerring2020population}.

@@

\vspace{.2cm}
The decision was based both on the relevance of these variables and due to data availability. We explain our decision on \textbf{page XXX}: XXX. We thank R1 for the opportunity to clarify the selection of these two central variables to our paper.
\vspace{.5cm}

@@

We agree with R1 that needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}. We also reference it \textbf{on pages 17 and 22 (footnote 13)} in the main article.

@@

\vspace{.2cm}
\textbf{We now show the analysis without the dummy variable (page XXX) for the northeast region in the main paper and move the regressions with the dummy to the Appendix (page XXX).} The results are virtually the same. We agree with R1 that the inclusion of the dummy variable might generate unecessary confusion and are not central to our argument. \textbf{Therefore, we also explain on page XXX why we included the dummy variable for the northeast region on page XXX}: XXX. Gilligan and Matsusaka.

@@

\vspace{.2cm}
We agree with R2 that the testing of the proposed mechanism is an extremelly interesting project for a follow-up article. In our \textbf{conclusion, on page 27,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."

@@

\vspace{.2cm}
We collapse two paragraphs from R3 since they speak to core topics in our paper. \textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly. Therefore, our results speak more about the allocation of resources than on public spending. \textbf{On page 15, in the Background on the Brazilian Case Section,} we clarify why increasing the city council size usually results in a pro-mayor legislator. "Additionally, Brazil's formula for apportioning legislative seats (a combination of the Hara quota and the D'Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat. As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p. 68]{Ames2001}. Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition." See also \textbf{footnote 12, on page 21-22.} Unfortunately, we could not find evidence that an extra-legislator improves descriptive representation in the city council, for instance, more female or non-white legislators \textbf{(see Table 4).} Finally, \textbf{in the Appendix, on page XX,} we show that the mayors' party is not driving the results.

@@

\vspace{.2cm}
We acknowledge that the external valitidy of our findings might be conditional on the time period or related to contexto characteristics of our study. \textbf{On page 5,} we write: "\citet{frey2021legislature}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage." \textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect. \citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways. These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment." Additionally, \textbf{in the Discussion Section, on page 27,} we write about the implications of our findings beyond Brazil. In this paragraph, we added the following sentence: "However, as the [...]"

>>>>

---

We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript. We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result. Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews. We adopt the following conventions:

\begin{itemize}
\item Suggestions identified in reviewers' reports are in \textit{italicized text}. We provide direct quotations of their reviewers' reports, lightly edited for clarifications or to conserve space.
\item Our responses to the reviewers' suggestions are in standard text.
\item The specific locations in the manuscript and online Appendix where incorporated
revisions can be found are shown in \textbf{bold text}.
\end{itemize}

@@

\vspace{.2cm}
We thank reviewer 1 for these two relevant additions. We cite \citet{GilliganMatsusaka2001}'s article \textbf{on page 7:} "Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways."   The Population and Politics book citation is \textbf{on page 6:} "However, legislature size does not \textit{necessarily} assure representativeness" \citep[p. 85]{gerring2020population}.

@@

\vspace{.2cm}
We thank R1 for the opportunity to clarify the selection of these two central variables for our paper. We explain our decision on \textbf{page 17}: "Access to basic education and health care are relevant goals to developing countries. For instance, according to Brazil's 1988 Constitution, municipalities have to spend 25\% of their budget on education and 15\% on health care. Consequently, the Health Ministry Data Service and the Ministry of Education Data Service provide readily available quality data on health care and education."

@@

We agree with R1 that we needed to provide more information on the online survey. Therefore, we detailed our procedures in the \textbf{Appendix Section A.14, on pages 22-23}. We also reference it \textbf{on pages 17 and 22 (footnote 13)} in the main article.

@@

\vspace{.2cm}
\textbf{FALTA FAZER: Dummy para a região Nordeste: estimar os modelos sem a dummy e reportar este resultado no artigo. Corrigir as menções aos coeficientes caso eles mudem. Colocar as regressões com a dummy no apêndice.}

@@

\vspace{.2cm}
We agree with R2 that testing the proposed mechanism is an extremely exciting project for a follow-up article. In our \textbf{conclusion, on page 29,} we write: "Future research should also evaluate whether an extra-legislator is helping the mayor in her competition for state or federal transfers, as proposed by \citet{catalinac2020tournament}."

@@

\vspace{.2cm}
\textbf{FALTA COMPLETAR:} We collapse two paragraphs from R3 since they speak to core topics in our paper. \textbf{In the Appendix Table XXX, on page XXX,} we show that an extra-legislator usually does not increase the municipal spending significantly. Therefore, our results speak more about the allocation of resources than on public spending. \textbf{On page 15, in the Background on the Brazilian Case Section,} we clarify why increasing the city council size usually results in a pro-mayor legislator. "Additionally, Brazil's formula for apportioning legislative seats (a combination of the Hara quota and the D'Hondt method) is an obstacle to small parties or coalitions attaining the electoral quotient that might give them a legislative seat. As a result, they often ally with larger coalitions so that they can reach the electoral quotient \citep[p. 68]{Ames2001}. Being a central political figure in the municipality, often the mayor is also a member of the most voted coalition." See also \textbf{footnote 12, on page 21-22.} Unfortunately, we could not find evidence that an extra-legislator improves descriptive representation in the city council, for instance, more female or non-white legislators \textbf{(see Table 4).} Finally, \textbf{in the Appendix, on page XX,} we show that the mayors' party is not driving the results.

@@

\vspace{.2cm}
We acknowledge that the external validity of our findings might be conditional on the contextual characteristics of our study. \textbf{On page 6-7,} we acknowledge that "since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect. \citet{frey2021legislature} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. Yet, \citet{GilliganMatsusaka2001} finds that in the US legislature size is associated primarily with higher spending on geographically concentrated benefits, such as education and highways. These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment."
Additionally, \textbf{in the Discussion Section, on page 29,} we write about the implications of our findings beyond Brazil. In this paragraph, we added the following new sentence: "As a caveat, our results might not be externally valid under different institutional norms (e.g., election rules or methods to allocating legislative seats) or at other governmental levels (federal or state). The findings presented here might also not be linear, since the impact of an extra-legislator should be heterogeneous depending upon the size of different legislatures or jurisdictions."

### 2022-03-11 article/article.Rmd
update AJPS revision

The last set of variables quantify social welfare. Our focus is on the impact of legislature size on education and health care, which are the two most important public services the municipal government should provide to citizens. We measure access to education with the average enrollment in primary (K--4) municipal public schools. We assess education quality with the Education Development Index (Índice de Desenvolvimento da Educação Básica--IDEB), which the Ministry of Education has issued biannually since 2007. The index is a weighted average of student scores in Portuguese and Mathematics (0--10), multiplied by the harmonic mean of public school promotion rates in a given year (0--100). To test the effect of the 2004 ruling on health care, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age. The source of all health care variables is the Brazilian Ministry of Health Data Center (DataSUS).

@@

Our findings have implications that extend well beyond Brazil. A general form of our argument is that it is easy for a politician to negotiate with members of her in-group \citep{abbink2019, g9030057}. Specifically, several countries have divisions between Executive and Legislative, such as the federal level of presidential systems, state governments, and local city councils. As these political bodies are influenced by political allegiances, the dynamics we expose here generalize to most of them. Depending on legislative support, changing legislature size could increase the chance of electing politicians that are not aligned with the Executive, decreasing welfare. Despite the particular effects on political support and welfare, the logic described in this paper would remain relevant for empirically accessing the welfare effects of enlarged legislatures. Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}.

>>>>

The last set of variables quantify social welfare. Our focus is on the impact of legislature size on education and health care, which are the two most important public services the municipal government should provide to citizens. \textbf{Access to basic education and health care are relevant goals to developing countries. For instance, according to Brazil's 1988 Constitution, municipalities have to spend 25\% of their budget on education and 15\% on health care. Consequently, the Health Ministry Data Service and the Ministry of Education Data Service provide readily available quality data on health care and education.} We measure access to education with the average enrollment in primary (K--4) municipal public schools. We assess education quality with the Education Development Index (Índice de Desenvolvimento da Educação Básica--IDEB), which the Ministry of Education has issued biannually since 2007. The index is a weighted average of student scores in Portuguese and Mathematics (0--10), multiplied by the harmonic mean of public school promotion rates in a given year (0--100). To test the effect of the 2004 ruling on health care, we collect data on infant mortality per thousand children born and on postneonatal infant mortality, which is the death of infants who survived more than 28 days, but died before reaching one year of age. The source of all health care variables is the Brazilian Ministry of Health Data Center (DataSUS).

@@

Our findings have implications that extend well beyond Brazil. A general form of our argument is that it is easy for a politician to negotiate with members of her in-group \citep{abbink2019, g9030057}. Specifically, several countries have divisions between Executive and Legislative, such as the federal level of presidential systems, state governments, and local city councils. As these political bodies are influenced by political allegiances, the dynamics we expose here generalize to most of them. Depending on legislative support, changing legislature size could increase the chance of electing politicians that are not aligned with the Executive, decreasing welfare. Despite the particular effects on political support and welfare, the logic described in this paper would remain relevant for empirically accessing the welfare effects of enlarged legislatures. Additionally, our findings may help us understand why other countries in Latin America and Asia can generate effective governance despite having strong executives and large coalitions \citep{pereira2012surprising}. \textbf{As a caveat, our results might not be externally valid under different institutional norms (e.g., election rules or methods to allocating legislative seats) or at other governmental levels (federal or state). The findings presented here might also not be linear, since the impact of an extra-legislator should be heterogeneous depending upon the size of different legislatures or jurisdictions.}
